\documentclass[letter,10pt]{article}
\usepackage{TLCresume}
\begin{document}

% %====================
% % EXPERIENCE F
% %====================

\subsection{{Univeristy of California, Irvine Summer Seminer \hfill 06/2022 --- 10/2022}}
\subtext{\textbf{Supervisor:} Associate Prof. Zhiying Wang at Univeristy of California, Irvine \hfill Universiry of California, Irvine, US}
\begin{zitemize}
\item \textbf{Research Topic:} \textit{Optimization of Federated Learning Aggregation Algorithms}
\item Gain experience for the research of Federated Learning.
\item Learned how to start an individual research project.
\item Build a new Federated Learning Aggregation Algorithm which has a better performance than the existing algorithms under Byzanitne Attack.
\end{zitemize}

% %====================
% % EXPERIENCE E
% %====================
\subsection{{Benchmarking Deep Learning Text Classification NLP Models \hfill 06/2022 --- 10/2022}}
\subtext{\textbf{Supervisor:} Associate Prof. Stuart Middleton at University of Southampton \hfill Universiry of Southampton, UK}
\begin{zitemize}
\item Working with a team of researchers to build a new Deep Learning classification model for the SafeSpaceNLP domain.
\item Gain more experience in the field of Natural Language Processing and Deep Learning.
\item Annotated a reddit dataset for the SafeSpaceNLP domain.
\end{zitemize}

% %====================
% % EXPERIENCE D
% %====================
\subsection{{Member of the Paper Writing Group Targeting ACM Survey (CSUR) \hfill 02/2022 --- 10/2023}}
\subtext{\textbf{Supervisor:} Associate Prof. Stuart Middleton at University of Southampton \hfill Universiry of Southampton, UK}
\begin{zitemize}
\item Gained experience of writing a systematic review paper
\item Establish the basic knowledge framework of Natural Language Processing in Hate Speech Detecting Area
\item Learned how to cooperate with each other in a research group
\end{zitemize}

%====================
% EXPERIENCE A
%====================
\subsection{{Deep Learning Online Training Project \hfill 11/2021 - 01/2022}}
\subtext{\textbf{Supervisor:} Associate Prof. Mark Vogelsberger at MIT \hfill Online Module}
\begin{zitemize}
\item Learned deep learning algorithms such as CNN, RNN, and GAN
\item Collaborated with the team to develop a model for diagnosing and identifyinglesions in lung cancer by processing the lung cancer image using the signal spectrum analysis first, and then combining it with the CNN algorithmtoimprove accuracy
\item Established different CNN models in TensorFlow and adjusted parameters toimprove diagnostic accuracy
\item Completed the Algorithms and Techniques, Model Evaluation and Validation, and Justification parts of the written report
\end{zitemize}

%====================
% EXPERIENCE B
%====================
\subsection{{President/Legal Representative \hfill 08/2021 –-- 10/2023}}
\subtext{Shanghai Ruoting Trading Co., LTD \hfill Shanghai, China}
\begin{zitemize}
\item Acting as a commercial agent to resell domestic high-quality electronic products overseas, and as a product procurement channel for large domestic companies (cross-border e-commerce)
\item Having established channel agent partnerships with three local brands
\end{zitemize}

\subsection{{President/Legal Representative \hfill 10/2023 –-- Present}}
\subtext{LandVertex (Shanghai) Co., LTD \hfill Shanghai, China}
\begin{zitemize}
\item Providing SOTA AI solutions for the real estate industry
\item Practice the concept of "AI + Real Estate" and "AI + Property Management"
\end{zitemize}
%====================
% EXPERIENCE C
%====================

% %====================
% % EXPERIENCE D
% %====================
% \subsection{{ROLE / PROJECT D \hfill MMM YYYY --- MMM YYYY}}
% \subtext{company D \hfill somewhere, state}
% \begin{zitemize}
% \item Vestibulum accumsan massa quis dignissim faucibus.
% \item Maecenas suscipit mi ut ullamcorper pharetra.
% \item In vitae ligula tristique, iaculis tortor in, egestas magna.
% \item In fringilla purus malesuada lectus imperdiet pulvinar.
% \item Nulla eu dolor congue, mollis dui a, eleifend purus.
% \end{zitemize}

%====================
% EXPERIENCE E
%====================
%\subsection{{ROLE / PROJECT E \hfill MMM YYYY --- MMM YYYY}}
%\subtext{company E \hfill somewhere, state}
%\begin{zitemize}
%\item In lobortis libero consectetur eros vehicula, vel pellentesque quam fringilla.
%\item Ut malesuada purus at mi placerat dapibus.
%\item Suspendisse finibus massa eu nisi dictum, a imperdiet tellus convallis.
%\item Nam feugiat erat vestibulum lacus feugiat, efficitur gravida nunc imperdiet.
%\item Morbi porta lacus vitae augue luctus, a rhoncus est sagittis.
%\end{zitemize}

\end{document}